Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-09-15 drafts/outline.tex
should be merged OK?
started intro section

%\setcounter{chapter}{1}

@@

\section{Environmental Significance}

>>>>

@@

\section{Riverine and Estuarine Ecohydraulics}

In fluvial aquatic environments, plant communities, sediment budgets, and flow patterns share a complex network of interactions and feedbacks across a wide range of spatial and temporal scales \citep{Wheaton_2011, Larsen_2019}. Recent research has highlighted the extent of these interactions across long distances \citep{van_2015_long},

% - 
%
%
%
%
%
